Minimizing post-shock forecasting error using disparate information

### 2020-07-03 manuscript/manuscript.tex
addition of Section 3.4 and many revisions to abstract, intro, and Section 3.3, 4, 5, 6

% function definition
\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\Hist}{\mathcal{H}}
\def\mbf#1{\mathbf{#1}} % bold but not italic
\def\ind#1{\mathrm{1}(#1)} % indicator function
\newcommand{\simiid}{\stackrel{iid}{\sim}} % IID 
\def\where{\text{ where }} % where
\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
\def\mrm#1{\mathrm{#1}} % remove math
\newcommand{\reals}{\mathbb{R}} % Real number symbol
\def\t#1{\tilde{#1}} % tilde
\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
\def\v#1{\mbi{#1}} % Vector notation
\def\mc#1{\mathcal{#1}} % mathical
\DeclareMathOperator*{\argmax}{arg\,max} % arg max
\DeclareMathOperator*{\argmin}{arg\,min} % arg min
\def\E#1{\mathrm{E}(#1)} % Expectation symbol
\def\var#1{\mathrm{Var}(#1)} % Variance symbol
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
\newcommand\red[1]{{\color{red}#1}}

@@

Things to do:
\begin{enumerate}
  \item Need to add simulations. 
  \item $\mu_{\alpha}=2$, $X_{i,t}\sim \Gamma(1,2)$, $\delta_i, \gamma_i \sim \normal{1}{0.5}$
  \item $\sigma=10$ for the base case.
  \item $\sigma_{\alpha}= (5, 10, 25, 50, 100)$
  \item $\sigma= (5, 10, 25, 50, 100)$
\end{enumerate}

@@

\begin{enumerate}
  \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
\end{enumerate}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed conditions when our methodology works and estimators for risk-reduction quantities. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. The risk-reduction conditions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the conditions and risk-reduction quantities are estimated by parametric bootstrap. These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best, using estimates from bootstrap procedures. Our Monte Carlo simulation results show that  the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large. In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well. We now motivate our aggregation techniques.

@@

\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}
\label{section322}
According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
\begin{align*}
  \Delta_{\rm adj} 
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
\quad   \text{ and } \quad 
  \Delta_{\rm wadj} 
  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
\end{align*}
In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
\begin{align*}
 \Delta_{\rm IVW} 
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
\end{align*}

@@

In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction results, and estimate risk-reduction using plug-in approach in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

@@

Recall that  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ from Proposition \ref{unbiased}. Given the bootstrapped estimates of the variance, we can estimate the risk-reduction quantities in Section \ref{comparisons} using the estimates from the parametric bootstrap. For example, the $\Delta_{\rm adj}$ and its estimator $\hat{\Delta}_{\rm adj}$ are
\begin{align*}
  \Delta_{\rm adj} 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
  \hat{\Delta}_{\rm adj} 
 & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
\end{align*}
where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance for $\hat{\alpha}_{\rm adj}$. Suppose the $\hat{\Delta}_{\rm wadj}$ and $\hat{\Delta}_{\rm IVW}$ are estimators for $\Delta_{\rm wadj}$ and $\Delta_{\rm IVW}$, respectively. Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}_{\rm est}>0$ for $\text{est} \in \{\text{adj}, \text{wadj}, \text{IVW}\}$, and  the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities. Next, we discuss some potential problems of the bootstrap procedures.

@@

@@

Parameter setup of our simulations are detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers. If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.  Moreover, $T_i^*$ is randomly selected from $2p + 4$ to $T_i-1$. Those are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$. In that case, we do not consider such $b$ in computations of means and variances. Additionally, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.

In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$. We used 200 replications of Monte Carlo simulations and $B = 500$ for computation; and report means and standard errors for estimated quantities accordingly.

@@

Specifically, we verify the unbiasedness results in Proposition \ref{unbiased}, and consistency of our proposed risk-reduction propositions. We define the consistency by whether our risk-reduction propositions yield results that agree with the reality that can be known in the simulation. Suppose we make the decision to  accept $\hat{\alpha}$ for $\hat{\alpha}\in \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ if risk-reduction proposition reports that $\hat{\alpha}$ reduces the risk, and reject $\hat{\alpha}$ otherwise. Consistency can be interpreted in a similar way to hypothesis testing with the following confusion table. 
\begin{center}
  \begin{center}
      \begin{tabular}{cc|c|c}
        \hline
        & & \multicolumn{2}{c}{Decision} \\
        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
                \hline
     \multirow{2}{*}{Truth}  & $R_{T_1^*+1,2}<R_{T_1^*+1,1}$ & Consistent & Inconsistent\\
      \cline{3-4}
      & $R_{T_1^*+1,2}>R_{T_1^*+1,1}$   & Inconsistent & Consistent \\
      \hline
      \end{tabular}
  \end{center}
\end{center}
We report 1 for risk-reduction propositions to be consistent and 0 otherwise. Recall that in Section \ref{comparisons}, we could estimate the risk-reduction quantities, and therefore select the best estimator with the maximum risk-reduction quantities. It is also possible to confirm whether this decision is true in a simulation setting. Similarly, we report 1 for the decision of selecting the best shock-effect estimators  to be consistent and 0 otherwise.

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{1, 5, 10, 25, 100\}$ where we fix $\sigma$ to 1. The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown. It is shown in Table ? that as the donor pool size increases, the bias and consistency results improve with more precision. In contrast, the result gets poorer as  the variance of $\alpha_i$ increases. It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$. Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates. But it is reversed in the random design case. Moreover, notice that the consistency for voting the best estimator works poor when $n$ is small but improves significantly when $n$ is large.

@@

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
    Leave-one-out consistency & 0.000 & 0.800 & 0.000
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

>>>>

% function definition
\newcommand{\R}{\mathbb{R}}
\newcommand{\w}{\textbf{w}}
\newcommand{\x}{\textbf{x}}
\newcommand{\X}{\textbf{X}}
\newcommand{\Y}{\textbf{Y}}
\newcommand{\Hist}{\mathcal{H}}
\def\mbf#1{\mathbf{#1}} % bold but not italic
\def\ind#1{\mathrm{1}(#1)} % indicator function
\newcommand{\simiid}{\stackrel{iid}{\sim}} %[] IID 
\def\where{\text{ where }} % where
\newcommand{\indep}{\perp \!\!\! \perp } % independent symbols
\def\cov#1#2{\mathrm{Cov}(#1, #2)} % covariance 
\def\mrm#1{\mathrm{#1}} % remove math
\newcommand{\reals}{\mathbb{R}} % Real number symbol
\def\t#1{\tilde{#1}} % tilde
\def\normal#1#2{\mathcal{N}(#1,#2)} % normal
\def\mbi#1{\boldsymbol{#1}} % Bold and italic (math bold italic)
\def\v#1{\mbi{#1}} % Vector notation
\def\mc#1{\mathcal{#1}} % mathical
\DeclareMathOperator*{\argmax}{arg\,max} % arg max
\DeclareMathOperator*{\argmin}{arg\,min} % arg min
\def\E#1{\mathrm{E}(#1)} % Expectation symbol
\def\var#1{\mathrm{Var}(#1)} % Variance symbol
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} % checkmark
\newcommand\red[1]{{\color{red}#1}}

@@

Things to do:
\begin{enumerate}
  \item Need to add simulations. 
\end{enumerate}

@@

\begin{enumerate}
  \item Revisions to abstract, introduction, simulation, data analysis, and discussions.
  \item Addition of Section 3.4
\end{enumerate}

@@

\maketitle
\begin{abstract}
    We developed a forecasting methodology for providing credible forecasts for time series data that has undergone a shock  by borrowing knowledge from disparate time series that have undergone similar shocks for which post-shock outcome is recorded. Three shock-effects estimators were constructed for minimizing average forecast risk. We proposed risk-reduction propositions providing conditions when our methodology works and estimators for risk-reduction quantities. Bootstrap procedures are provided to estimate the variability of our shock effect estimators; and these procedures can be used to assess the potential success of post-shock prediction before the post-shock response is observed. The risk-reduction propositions and risk-reduction quantities are powerful tools for users because we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best. Leave-one-out cross validation with $k$ random  draws is proposed to estimate consistency of risk-reduction propositions and best consistency of voting the best shock-estimators, prospectively informing users the probabilities that this prospective evaluation is consistent with the reality. Several simulated data examples, and a real data example of forecasting Conoco Phillips stock price are provided for verification and illustration.
\end{abstract}

@@

We consider three aggregation techniques: simple averaging, inverse-variance weighted averaging, and similarity weighting. The latter technique is similar to the weighting in synthetic control methodology \citep{abadie2010synthetic}. We provide risk-reduction propositions that detail the conditions  when the adjusted forecasts will work better than the original one, and estimate risk-reduction quantities to find the best technique out of the three. The involved parameters in the risk-reduction propositions and risk-reduction quantities are estimated by parametric bootstrap. These propositions and risk-reduction quantities are powerful tools for users in the sense that we can empirically aid a prospective evaluation about whether the three aggregation techniques  will work well and which one is the best, using estimates from bootstrap procedures. Furthermore, to inform the credibility of this prospective evaluation, we propose a leave-one-out cross validation with $k$ random draws to estimate the consistency of the risk-reduction propositions and best consistency of voting the best shock-effect estimators prospectively (see Definition \ref{consistency} and \ref{best consistency}), which tell the probabilities that the prospective evaluation is consistent with the reality. Our Monte Carlo simulation results show that  the risk-reduction conditions are highly consistent with the truth when the model for the shock effects is identified well with appropriate covariates under a fixed design; and gain more precision when the donor pool size increases. Our simulations further show that the procedure of voting the best technique by risk-reduction quantities is consistent with the truth when donor pool size is large. In the real data example of forecasting stock price of Conoco Phillips that experienced a shock on 2020 March 9th, the proposed three aggregation techniques work decently well. We now motivate our aggregation techniques.

@@

\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}
\label{section322}
According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
\begin{align*}
  \Delta(\hat{\alpha}_{\rm adj})
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
\quad   \text{ and } \quad 
  \Delta(\hat{\alpha}_{\rm wadj})
  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
\end{align*}
In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
\begin{align*}
 \Delta(\hat{\alpha}_{\rm IVW})
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
\end{align*}

@@

In this section, we present a bootstrap procedure that approximates the distribution of our shock-effect estimators, checks the underlying conditions of our risk reduction propositions, and estimate risk-reduction using plug-in approach in practice. Our procedure involves the resampling of residuals in the separate OLS fits. This procedure has its origins in Section 6 of \citet{efron1986bootstrap}, and it involves the resampling the residuals which are assumed to be the realizations of an iid processes.
%NO NEED TO OUTLINE IN THIS WAY: In the first step, we will introduce the pros and cons of this algorithm and refer the users to other alternatives. In the second step, we detail the procedure of boostrapping AR(1).
%%\citet{efron} introduces the bootstrapping method to approximate the distribution of a statistic using a \emph{random sample}. However, this method will fail for time-series data since serial correlation or time-dependent features exist in typical time-series model. 
%In the AR($p$) model, the unobserved errors are assumed to be identically and independently distributed. In this setting, standard bootstrap methodology can be applied to resampling the residuals \citep{efron1986bootstrap}. 
\citet{bose1988edgeworth} showed that the asymptotic accuracy for OLS parameter estimation can be further improved from $O(T^{-1/2})$ to $o(T^{-1/2})$ almost surely under some regularity conditions.

@@

Recall that  $\hat{\alpha}_{\rm wadj}$ and $\hat{\alpha}_{\rm IVW}$ are unbiased estimators of their expectations, and $\hat{\alpha}_{\rm wadj}$ is an unbiased estimator of $\E{\alpha_1}$ from Proposition \ref{unbiased}. Given the bootstrapped estimates of the variance, we can estimate the risk-reduction quantities in Section \ref{comparisons} using the estimates from the parametric bootstrap. For example, the $\Delta_{\rm adj}$ and its estimator $\hat{\Delta}_{\rm adj}$ are
\begin{align*}
  \Delta(\hat{\alpha}_{\rm adj})
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
  \hat{\Delta}(\hat{\alpha}_{\rm adj})
 & = (\hat{\alpha}_{\rm wadj})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\hat{\alpha}_{\rm adj}-\hat{\alpha}_{\rm wadj})^2,
\end{align*}
where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance for $\hat{\Delta}(\hat{\alpha}_{\rm adj})$.

Suppose we have a pool of shock-effect estimators, $\mc{A}$, e.g., $\mc{A}= \{\hat{\alpha}_{\rm adj}, \hat{\alpha}_{\rm wadj}, \hat{\alpha}_{\rm IVW}\}$ in our study. We can determine which one is the best shock-effect estimator. Suppose the $\hat{\Delta}(\hat{\alpha}_{\rm wadj})$ and $\hat{\Delta}(\hat{\alpha}_{\rm IVW})$ are estimators for $\Delta(\hat{\alpha}_{\rm wadj}) $ and $\Delta(\hat{\alpha}_{\rm IVW})$, respectively. Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}(\hat{\alpha})>0$ for $\hat{\alpha}\in \mc{A}$. Besides, we can also select the best shock-effect estimator accordingly. Define
\begin{align}
	\hat{\alpha}_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \hat{\Delta}(\hat{\alpha}) \quad \text{ and } \quad  \alpha_{\rm best} = \argmax_{\hat{\alpha}\in \mc{A}} \Delta(\hat{\alpha}). \label{best}
\end{align}
That is, the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities whereas $\alpha_{\rm best}$ is the true best shock-effect estimator given observed post-shock response. See more discussions in Section \ref{loocv}.

@@

\subsection{Leave-one-out cross validation with $k$ random draws}
\label{loocv}

In this section, we introduce a powerful procedure for rendering prospective evaluations of the applicability of the proposed methods. First, we introduce the concept of consistency. Second, we detail the leave-one-out cross-validation with $k$ random draws to realize the estimation prospectively.

Our risk-reduction propositions methodologies can be evaluated by \emph{consistency}. Risk-reduction propositions are decision-making procedures that might commit a type of error, which is similar to Type I or Type II error in a hypothesis test. Let $\hat{\alpha}$ be an estimator of $\alpha_1$ and $\delta_{\hat{\alpha}}$ is the corresponding risk-reduction proposition. If $\Delta(\hat{\alpha})>0$ ($\Delta(\hat{\alpha})<0$, respectively) but $\delta_{\hat{\alpha}}$ incorrectly reported $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) so that it make the decision not to use $\hat{\alpha}$ (to use $\hat{\alpha}$, respectively), $\delta_{\hat{\alpha}}$ is said to be \emph{inconsistent}. If $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) and  $\delta_{\hat{\alpha}}$ correctly reported $\Delta(\hat{\alpha})<0$ ($\Delta(\hat{\alpha})>0$, respectively) so that it make the decision to use $\hat{\alpha}$, $\delta_{\hat{\alpha}}$ is said to be \emph{consistent}. These situations are depicted in the following table. 
\begin{center}
  \begin{center}
      \begin{tabular}{cc|c|c}
        \hline
        & & \multicolumn{2}{c}{Decision} \\
        & & Use $\hat{\alpha}$ & Do not use $\hat{\alpha}$ \\ 
                \hline
     \multirow{2}{*}{Truth}  & $\Delta(\hat{\alpha})>0$ & Consistent & Inconsistent\\
      \cline{3-4}
      & $\Delta(\hat{\alpha})<0$  & Inconsistent & Consistent \\
      \hline
      \end{tabular}
  \end{center}
\end{center}
Similar definitions can be adapted to the best shock-effect estimators.

In this setting, judging whether $\delta_{\alpha}$ is consistent can be treated as a Bernoulli trial that reports 1 if $\delta_{\alpha}$ is consistent, and reports 0 if $\delta_{\alpha}$ is inconsistent. It is also true for selecting the best shock-effect estimator. It motivates us to define
\begin{align*}
	\mc{C}(\delta_{\alpha}) 
	= I(\delta_{\hat{\alpha}} \text{ is consistent})
 \quad \text{ and } \quad  	
 \mc{C}(\mc{A}) 
	= I(\hat{\alpha}_{\rm best} = \alpha_{\rm best})
\end{align*}
where $I(\cdot)$ is an indicator function, $\mc{A}$ is the pool of shock-effect estimators, $\alpha_{\rm best}$ is the true best shock-effect estimator, and $\hat{\alpha}_{\rm best}$ is the best shock-effect estimator selected by the maximum estimated risk-reduction,   see Section \ref{varbootstrap}.  Then, we can define consistency and best consistency as in Definition \ref{consistency} and \ref{best consistency}.

\begin{defn}
\normalfont 	\label{consistency}The \emph{consistency} of 	the risk-reduction proposition $\delta_{\hat{\alpha}}$ is $\E{\mc{C}(\delta_{\hat{\alpha}})}$.
\end{defn}

\begin{defn}
	\normalfont  \label{best consistency}Given $\mc{A}$ the pool of shock-effect estimators, the \emph{best consistency} is $\E{\mc{C}(\mc{A})}$.
\end{defn}
Consistency and best consistency are important parameters for users to evaluate the effectiveness of our risk-reduction propositions and estimated risk-reduction. If $\E{\mc{C}(\delta_{\hat{\alpha}})} > 0.5$, we  claim that $\delta_{\hat{\alpha}}$ is better than a random guess. If $\E{\mc{C}(\mc{A})} > 1/ |\mc{A}|$, we claim that the procedure of selecting the best shock-effect estimators is better than a random guess. Note that $\mc{C}(\delta_{\hat{\alpha}})$
 and $\mc{C}(\mc{A})$ generally can be known only if the post-shock response is observed. But it is only feasible in a retrospective finding. It is even more difficult to construct a random sample to estimate $\E{\mc{C}(\delta_{\hat{\alpha}})}$ or $\E{\mc{C}(\mc{A})}$. Nevertheless, it is possible to estimate them using the procedure \emph{leave-one-out cross validation (LOOCV)}.

Our proposed LOOCV tailors the standard LOOCV to our application. See details of standard LOOCV in Section 7.10 of \citet{hastie2009elements}.  Recall in Section \ref{modelsetup} that we are given the data $\{(\mbf{x}_{i,t}, y_{i,t}) \colon i = 1, \ldots, n+1, t = 1, \ldots, T_i\}$, where $\{(\mbf{x}_{1,t}, y_{1,t})\colon t = 1, \ldots, T_1\}$ is the data of the time series of interest and the remaining is those of the donor pool. For $m^{\rm th}$ iteration of LOOCV, where $m = \{1, \ldots, n\}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$. Since the post-shock response $y_{m+1, T_{m+1}^*+1}$ is observed, for $\hat{\alpha}\in \mc{A}$, we can compute the consistency and best consistency as $\mc{C} ^{(-m)}(\delta_{\hat{\alpha}})$ and $\mc{C} ^{(-m)}(\mc{A})$  using the estimation procedures in Section \ref{varbootstrap}. The the LOOCV estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$  and $\E{\mc{C}(\mc{A})}$ are
\begin{align*}
	 \bar{\mc{C}}(\delta_{\hat{\alpha}})= \frac{1}{n} \sum_{m = 1}^n \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})
	 \quad \text{ and } \quad \bar{\mc{C}}(\mc{A})= \frac{1}{n} \sum_{m = 1}^n \mc{C} ^{(-m)}(\mc{A}).
\end{align*}
Note that to satisfy $\mc{M}_{2}$ in Section \ref{modelsetup}, the candidates from donor pool has to be assumed to be mutually independent. Based on this assumption, $\bar{\mc{C}}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively \citep[Page 222]{msos}.

However, LOOCV can be very computationally intensive when $n$ is large. In an analog to $k$-fold cross-validation as remedies for ordinary LOOCV, we propose a similar procedure \emph{LOOCV with $k$ random draws} to alleviate the computation burden. LOOCV with $k$ random draws differs in the selection of indices. The algorithms are outlined as follows. If $n \leq  k$, we set $k$ to be $n$. If $n > k$, we randomly sample without replacement $k$ elements from $\{1, \ldots, n\}$ to gather them into $\mc{J}$. For $m \in \mc{J}$, we set aside $\{(\mbf{x}_{m + 1, t}, y_{m + 1, t}) \colon t = 1, \ldots, T_{m+1}\}$ as the time series of interest, and construct a new donor pool $\{(\mbf{x}_{i, t}, y_{i, t}) \colon i \in \mc{I}, t = 1, \ldots, T_{i}\}$, where $\mc{I}=\{2, \ldots, n+1\} \setminus \{m+1\}$. The LOOCV with $k$ random draws estimates for $\E{\mc{C}(\delta_{\hat{\alpha}})}$  and $\E{\mc{C}(\mc{A})}$ are
\begin{align*}
	 \bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\delta_{\hat{\alpha}})
	 \quad \text{ and } \quad \bar{\mc{C}}^{(k)}(\mc{A})= \frac{1}{k} \sum_{m \in \mc{J}} \mc{C} ^{(-m)}(\mc{A}).
\end{align*}
Similarly, assuming the candidates in the donor pool are  mutually independent and the data  satisfy $\mc{M}_{2}$, $\bar{\mc{C}}^{(k)}(\delta_{\hat{\alpha}})$ and $\bar{\mc{C}}^{(k)}(\mc{A})$ should be almost unbiased estimates of $\E{\mc{C}^{}(\delta_{\hat{\alpha}})}$ and $\E{\mc{C}(\mc{A})}$, respectively. The estimation bias should decrease as $k \to n$.  In practice, $k=5$ or $k=10$ can be typical choices for LOOCV with $k$ random draws.

@@

Parameter setup of our simulations are detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers. If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.  Moreover, $T_i^*$ is randomly selected from $2p + 4$ to $T_i-1$. Those are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$. In that case, we do not consider such $b$ in computations of means and variances. Additionally, we generated the covariates from $\Gamma(1,2)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.

In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$. We used $30$ replications of Monte Carlo simulations and $B = 200$ for computation; and report means and standard errors for estimated quantities accordingly. $k=5$ is set up for LOOCV with $k$ random draws.

@@

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{5, 10, 25, 50, 100\}$ where we fix $\sigma$ to $10$. From Table ?, assuming that $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ well estimates $\E{\mc{C}(\delta_{\hat{\alpha}}})$ and fixing $n$, we can observe that $\delta_{\hat{\alpha}}$ is highly consistent for $\hat{\alpha}\in \mc{A}$ when $\sigma_{\alpha}$ is small. It is because when $\sigma_{\alpha}$ is small, the signal of the covariates is strong so that $\hat{\alpha}_{\rm wadj}$ will be expected to capture the signal. Moreover, when $\sigma_{\alpha}$ is small, $\mc{M}_{22}$ approximates $\mc{M}_{21}$ such that estimation of $\E{\alpha_1}$ should be nearly unbiased according to Proposition \ref{unbiased}. Nevertheless, when the signal of the covariates is poor ($\sigma_{\alpha}$ is big), the $\delta_{\hat{\alpha}}$  become more inconsistent for $\hat{\alpha}\in \mc{A}$. It is to be expected since the bootstrap estimates become more biased. However, users can be warned by $\bar{C}^{(k)}(\delta_{\hat{\alpha}})$ to have an idea of the effectiveness of $\delta_{\hat{\alpha}}$. Fixing $\sigma_{\alpha}$, we can observe that $\delta_{\hat{\alpha}}$ becomes more consistent when $n$ increases. It is due to the robustness gain in estimation when $n$ increases.

In this setting, comparing Table ? with Table ??, we can see that $\mc{B}_u$ does not differ a lot from $\mc{B}_c$.

@@

\begin{table}[H]
  \caption{Bootstrap estimates and results yielded by risk-reduction propositions with $B = 1000$}\label{table2}
  \begin{center}
    \begin{tabular}{lrrr}
      & $\hat{\alpha}_{\rm adj}$ & $\hat{\alpha}_{\rm wadj}$ & $\hat{\alpha}_{\rm IVW}$ \\
      \hline 
    Bootstrapped variance & 0.531 & 0.479 & 0.970 \\
    \end{tabular}
  \end{center}  
\end{table}
\vspace{-.5cm}

Using $\mc{B}_c$ proposed in Section \ref{varbootstrap}, we estimated parameters for risk-reduction propositions and risk-reduction quantities proposed in  Section \ref{properties}; and the result is presented in Table \ref{table2}. Plugging these estimates into conditions in Section \ref{properties} and risk-reduction formulas in Section \ref{comparisons} yields (1) $\hat{\alpha}_{\text{adj}}$, $\hat{\alpha}_{\text{wadj}}$, and $\hat{\alpha}_{\text{IVW}}$  reduce the risk and (2) the risk-reduction quantities are $34.565$, $34.880$, and $34.139$, respectively.  The estimated risk-reduction quantities  vote $\hat{\alpha}_{\rm wadj}$  for the best estimator. LOOCV with $k$ random draws was not implemented since the effective $n$ is $3$, a number too small to provide a credible estimation. We verify the consistency of the result yielded by risk-reduction propositions with the reality as below.
